### 2017-02-07 manuscript.rmd
removed pdf indenting

---
bibliography: manuscript.bib
csl: nature.csl
output:
  pdf_document:
    dev: png
    fig_caption: yes
    fig_width: 6
    fig_height: 4
  github_document:
    fig_caption: yes
header-includes:
  - \setlength{\parindent}{4em}
---

>>>>

---
bibliography: manuscript.bib
csl: nature.csl
output:
  pdf_document:
    dev: png
    fig_caption: yes
    fig_width: 6
    fig_height: 4
  github_document:
    fig_caption: yes

---
